---
title: "Patchwork Analysis"
output: html_notebook
author: Kaia Newman
date: 04-11-2026
---


```{r}
# install required packages
# options(repos = list(CRAN="http://cran.rstudio.com/"))
# install.packages("knitr")
# install.packages("rmarkdown")
# install.packages("multcomp")
# install.packages("likert")
# install.packages("lmerTest")
# install.packages("parameters")
# install.packages("sqldf")
# install.packages("stargazer")
# install.packages("GGally")
# install.packages("broom.mixed")
# install.packages("patchwork")
# install.packages("ggpubr")
# install.packages("merDeriv")
# install.packages("AER")
# install.packages("effectsize")
# install.packages("tidyverse")
# install.packages("ggplot2")
# install.packages("performance")
# install.packages("lme4", type = "source")
# install.packages("moments")
install.packages("simr")
```

# Load libraries
```{r}
#load libraries
library(ggplot2)
library(dplyr)
library(lme4)
library(psych)
library(multcomp)
library(parameters)
library(performance)
library(car)
library("ARTool")
library(tidyverse)
```
# Read in analysis dataframe and preprocess columns
```{r}
# Make full df, gaze-valid df, full df had patch, gaze-valid had patch 
full_df = read.csv("timing_correctness_data.csv")

# Make boolean columns
full_df$correct = ifelse(full_df$correct == "Y", TRUE, FALSE)
full_df$had_patch = (full_df$condition == "overfitting" | full_df$condition == "correct")
# P2 t3 was cut off 5 minutes early
# make column for that, add to model, remove if not explanatory of much variance
full_df$cut_off = FALSE
full_df$cut_off[full_df$PID == 'P2' & full_df$task_no == 3] = TRUE

# Make other random effects factors
full_df$PID = as.factor(full_df$PID)
full_df$bug = as.factor(full_df$bug)
full_df$condition = as.factor(full_df$condition)

# make numPrev column
full_df$num_prev = full_df$task_no - 1
full_df$num_prev = as.factor(full_df$num_prev)

# For IDK in would_submit category, turn to NA
full_df$would_submit[full_df$would_submit == 'IDK'] = NA
# Also, blanks got read in as "" instead of NA
full_df$would_submit[full_df$would_submit == ""] = NA
full_df$think_patch_correct[full_df$think_patch_correct == ""] = NA
# Combine Y/P for self-reported data since they have the same valence
full_df$think_correct[full_df$think_correct == 'Y' | full_df$think_correct == 'P'] = 'YP'
full_df$think_patch_correct[full_df$think_patch_correct == 'Y' | full_df$think_patch_correct == 'P'] = 'YP'
full_df$would_submit[full_df$would_submit == 'Y' | full_df$would_submit == 'P'] = 'YP'

# Make columns for correct patch/fix judgments 
full_df$accurate_about_correctness = (full_df$correct == TRUE & full_df$think_correct == 'YP') | 
                                      (full_df$correct == FALSE & full_df$think_correct == 'N')
full_df$accurate_about_patch_correctness = (full_df$correct == TRUE & full_df$think_correct == 'YP') | 
                                      (full_df$correct == FALSE & full_df$think_correct == 'N')
```

# Prep data from survey to put in analysis dataframe
```{r}
# Add columns for in-study survey per participant-task
survey = read.csv("patchwork_survey.csv")

# Find duplicate PIDs and rename to P1-0 through P6-0
which(tolower(survey$Q24) == "p1")
survey$Q24[4] = "P1_0"
survey$Q24[5] = "P2_0"
survey$Q24[6] = "P3_0"
survey$Q24[7] = "P4_0"
survey$Q24[8] = "P5_0"
survey$Q24[9] = "P6_0"

# Q24 -- PID
# Q1_10 -- mental/perceptual activity
# Q2_1 -- time pressure
# Q3_1 -- performance
# Q4_1 -- effort
# Q5_1 -- frustration

# and so on for t2:
# Q44_10 -- mental/perceptual activity
# Q45_1 -- time pressure
# ...

# and for t3:
# Q50_10 -- mental/perceptual activity
# Q51_1 -- time pressure
# ...

# Create average cognitive load for t1, 2, and 3
data.frame(index = seq_along(survey), name = names(survey))
survey$Q24 = as.factor(survey$Q24)
# some people did not drag the scale and meant 0 -- change NaNs to 0. more accurate to what really happened than missing data
fill = function(x) replace(as.numeric(x), is.na(as.numeric(x)), 0)
survey[, 20:24] = lapply(survey[, 20:24], fill)
survey[, 26:30] = lapply(survey[, 26:30], fill)
survey[, 32:36] = lapply(survey[, 32:36], fill)


# level of performance (Q3_1, Q46_1, Q52_1) should be inverse
survey$Q3_1 = 21 - survey$Q3_1
survey$Q46_1 = 21 - survey$Q46_1
survey$Q52_1 = 21 - survey$Q52_1

survey$t1_cognitive_load = rowMeans(survey[, 20:24])
survey$t2_cognitive_load = rowMeans(survey[, 26:30])
survey$t3_cognitive_load = rowMeans(survey[, 32:36])

# Now set ONE column in timing_data which has these averages, matching with PID and task number
lookup = as.matrix(survey[, c("t1_cognitive_load", "t2_cognitive_load", "t3_cognitive_load")])
rownames(lookup) = survey$Q24

full_df$cognitive_load = lookup[
  cbind(
    match(full_df$PID, rownames(lookup)),
    full_df$task_no
  )
]

# TODO: maybe OCEAN personality data, but that's not on the critical path

# Chop off header in survey
survey = survey[4:nrow(survey), ]

# rename column to make easier to remember as predictor
survey = rename(survey, PID = Q24)

# Subset to self-efficacy. columns Q2_1.1, Q2_2--8
cols = c("Q2_1.1", "Q2_2", "Q2_3", "Q2_4", "Q2_5", "Q2_6", "Q2_7", "Q2_8")
se = survey[, cols]
# See all unique values across all your SE columns
lapply(se[cols], unique)
# Numericize and average
efficacy_map = c("Strongly Disagree" = 1,
                 "Somewhat disagree" = 2,
                 "Neither agree nor disagree" = 3,
                 "Somewhat agree" = 4,
                 "Strongly agree" = 5)
se[cols] = lapply(se[cols], function(x) efficacy_map[x])
survey$self_efficacy = rowMeans(se[cols], na.rm = TRUE)
# Add column to timing_data for self_efficacy
full_df = merge(full_df,
                    survey[, c("PID", "self_efficacy")],
                    by = "PID",
                    all.x = TRUE)
```

# Prep data from screener to put in analysis dataframe
```{r}
screener = read.csv("patchwork_screener.csv")

# Chop off header in screener
screener = screener[3:nrow(screener), ]

# rename column to make easier to remember as predictor
screener = rename(screener, professional_YOE = Q11)
screener$professional_YOE = as.numeric(screener$professional_YOE)
screener$PID = as.factor(screener$PID)

# Singleton category is problematic, so we'll say unemployed participant is recently in their professional career
screener$professional_identity = ifelse(
  screener$professional_identity == "Unemployed",
  "Professional",
  screener$professional_identity
)
# Also combine to "grad student"
screener$professional_identity = ifelse(
  screener$professional_identity == "PhD" | screener$professional_identity == "Masters",
  "Grad",
  screener$professional_identity
)
screener$professional_identity = as.factor(screener$professional_identity)
```

# Demographics of participants
```{r}
# Find demographics: min max median age and YOE
screener$Age = as.numeric(screener$Age)
paste0("Median age: ", median(screener$Age, na.rm=TRUE))
paste0("Minimum age: ", min(screener$Age, na.rm=TRUE))
paste0("Maximum age: ", max(screener$Age, na.rm=TRUE))

paste0("Median YOE: ", median(screener$professional_YOE, na.rm=TRUE))
paste0("Minimum YOE: ", min(screener$professional_YOE, na.rm=TRUE))
paste0("Maximum YOE: ", max(screener$professional_YOE, na.rm=TRUE))

# Q13 is gender, Q16 is are you a student (answers: Yes, I am a Master's student, Yes, I am a Ph.D. student, No, Yes, I am undergraduate), Q10 is have you worked or are you currently working... with "Yes, I currently work at one" being the professional label
as.data.frame(table(screener$Q13))
```

# RQ1a: Just run the models from APR, What is it Good For? (ICSE 2024)
```{r}
# Note: these are not our final models for this RQ, and were not derived in a principled way. We're just seeing how the models from the paper fare for us.
correctness_model = glmer(correct ~ condition + (1 |PID) + (1 | bug), data = full_df, family = binomial)

summary(correctness_model)

timing_model = lmer(time_minutes ~ condition + num_prev + (1 | PID) + (1 | bug), data = full_df)

summary(timing_model)

# Redo significance testing 
k1 <- glht(timing_model, mcp(condition="Tukey"))$linfct
k2 <- glht(timing_model, mcp(num_prev="Tukey"))$linfct
posthoc <- glht(timing_model, linfct = rbind(k1,k2))
summary(posthoc)
model_parameters(timing_model)

r2(timing_model)
Anova(timing_model)
```

# Check predictors for collinearity issues and merge
```{r}
# Q20 is IntelliJ IDEA IDE experience and Q21 is Java
# Subset screener to IntelliJ/Java experience
exp_vars = screener[, c("Q20", "Q21")]

exp_vars$Q20 = ifelse(screener$Q20 == "Not familiar at all",  1,
                      ifelse(screener$Q20 == "Slightly familiar",     2,
                             ifelse(screener$Q20 == "Moderately familiar",   3,
                                    ifelse(screener$Q20 == "Very familiar",         4,
                                           ifelse(screener$Q20 == "Extremely familiar",    5, NA)))))

exp_vars$Q21 = ifelse(screener$Q21 == "Not knowledgeable at all",  1,
                      ifelse(screener$Q21 == "Slightly knowledgeable",     2,
                             ifelse(screener$Q21 == "Moderately knowledgeable",   3,
                                    ifelse(screener$Q21 == "Very knowledgeable",         4,
                                           ifelse(screener$Q21 == "Extremely knowledgeable",    5, NA)))))

# estimates the correlation between two ordinal variables
polychoric(exp_vars)

# Average into single component, since they covary highly enough
screener$java_intellij_experience = rowMeans(exp_vars, na.rm = TRUE)

# if number is low, we can count years of experience and java_intellij_experience as different predictors, not impacting model collinearity
cor(screener$professional_YOE, screener$java_intellij_experience,
    use = "complete.obs", method = "spearman")

# Look at correspondence between professional identity and YOE
# Boxplot: Years of Experience by Professional Identity
boxplot(professional_YOE ~ professional_identity, data = screener,
        main = "YOE by Professional Identity",
        xlab = "Professional Identity",
        ylab = "Years of Experience")

# Means of YOE within each category
# PhD and Masters have similar average YOE, but have different professional identities, so it may be valuable to include this as a predictor
aggregate(professional_YOE ~ professional_identity,
          data = screener,
          FUN = mean)

# Add column to full_df for professional YOE, java_intellij_experience, professional identity
full_df = merge(full_df,
                    screener[, c("PID", "java_intellij_experience", "professional_YOE", "professional_identity")],
                    by = "PID",
                    all.x = TRUE)
```

# Subset dataframes for relevant analyses
```{r}
# FIXME: not necessarily required to look at source code, should find a better thing to subset on
gaze_valid_df = full_df[!is.na(full_df$Source.Code_fixation_count), ]

# boolean for whether they looked at the buggy method
gaze_valid_df$looked_at_buggy_method = ifelse(is.na(gaze_valid_df$ttff_buggy_method), FALSE, TRUE)
# FIXME: do we want to drop people who didn't look at the patch from this dataframe?

full_df_had_patch = full_df[full_df$had_patch, ]
# relevel bc no control
full_df_had_patch$condition = factor(full_df_had_patch$condition, 
                                       levels = c("correct", "overfitting"))
levels(full_df_had_patch$condition)

gaze_valid_had_patch = full_df_had_patch[!is.na(full_df_had_patch$Source.Code_fixation_count), ]
```

# RQ1a: How do patch suggestions affect time and accuracy of debugging sessions? (Section FIXME) 
```{r}
# TODO: read in 2024 data and see if our participants are significantly more correct/faster (try and understand expertise to give evidence for why we might be seeing different results/no trend)

# And now, as determined by the DAG, participant insights, and prior literature, we define the maximal model
# FIXED EFFECTS:
# key players: treatment condition, professional YOE. these are the ones we'll try nested models for in LRT.
# intellij/java experience
# self-efficacy scores
# number of previous tasks, looking for ordering effects 

# Note: my intuition is that professional YOE/professional identity are too related as constructs for what we're trying to measure (latent expertise) to include both
# in the same model

# We would include treatment condition * professional YOE (hypothesis from participants: professionals might be less affected by wrong patches) and some other interaction effects, but we don't really have enough samples to be able to do this

# RANDOM EFFECTS:
# bug, PID
# optimizer maybe helps the convergence some because it goes for more iterations

full_correctness_model = glmer(correct ~ condition + professional_YOE
                              + java_intellij_experience + self_efficacy + num_prev
                              + (1 | PID) + (1 | bug), 
                              data = full_df, 
                              family = binomial)

# Do LRT to see whether condition, professional_YOE, and professional_YOE:condition improve the model
correctness_model_no_condition = glmer(correct ~ professional_YOE
                              + java_intellij_experience + self_efficacy + num_prev
                              + (1 | PID) + (1 | bug), 
                              data = full_df, 
                              family = binomial)
condition_LRT = anova(full_correctness_model, correctness_model_no_condition)

correctness_model_no_YOE = glmer(correct ~ condition
                              + java_intellij_experience + self_efficacy + num_prev
                              + (1 | PID) + (1 | bug), 
                              data = full_df, 
                              family = binomial)
YOE_LRT = anova(full_correctness_model, correctness_model_no_YOE)

# BH-correct for multiple comparisons in LRTs and present results
p_vals = c(
  condition    = condition_LRT$`Pr(>Chisq)`[2],
  YOE          = YOE_LRT$`Pr(>Chisq)`[2]
)

p_adjusted = p.adjust(p_vals, method = "BH")

# print both together for easy comparison
data.frame(
  predictor = names(p_vals),
  p_raw     = p_vals,
  p_adj     = p_adjusted
)

# LRT results: YOE does not improve the model
# Summarize the best model to report
summary(correctness_model_no_YOE)

# Overall results:
# Correct patch suggestions predict solution correctness
# No evidence for overfitting patches making things worse

# Summary stats
summary(full_df$time_minutes)

# Look at distribution shape
# FIXME: survival analysis
hist(full_df$time_minutes, breaks = 30)

full_timing_model = glmer(time_minutes ~ condition + professional_YOE
                              + java_intellij_experience + self_efficacy + num_prev
                              + (1 | PID) + (1 | bug), 
                              data = full_df, 
                              family = Gamma(link="log"))

# Check residuals because of skewness 
residuals = resid(full_timing_model)
hist(residuals)
paste0("This is the skewness of the residuals: ", skewness(residuals))

# correcting for multiple comparisons for categorical predictors
k1 <- glht(timing_model, mcp(condition="Tukey"))$linfct
k2 <- glht(timing_model, mcp(num_prev="Tukey"))$linfct
posthoc <- glht(timing_model, linfct = rbind(k1,k2))
summary(posthoc)
model_parameters(timing_model)

r2(timing_model)
Anova(timing_model)

# TODO: Are professionals more likely to edit the patch they were given? Are students more likely to overfit? (passes tests x is incorrect for a new column of “overfitting_fix”)
```

# RQ1b: How do developer self-reports measure up to behavioral outcomes?
```{r}
# Tables to make: think correct vs. actually correct, think patch correct vs. patch condition, would submit vs. actually correct
correct_tab = table(full_df$correct, full_df$think_correct)
patch_correct_tab = table(full_df_had_patch$condition, full_df_had_patch$think_patch_correct)
submit_correct_tab = table(full_df$would_submit, full_df$correct)

as.data.frame.matrix(correct_tab)
as.data.frame.matrix(patch_correct_tab)
as.data.frame.matrix(submit_correct_tab)

test_patch = chisq.test(patch_correct_tab, simulate.p.value = TRUE, B = 10000)
test_correct = chisq.test(correct_tab, simulate.p.value = TRUE, B = 10000)
test_submit = chisq.test(submit_correct_tab, simulate.p.value = TRUE, B = 10000)

test_patch
test_correct
test_submit

# Standardized residuals (anything above 2 or below -2 is notable)
test_patch$stdres
test_correct$stdres
test_submit$stdres

# Notably, participants are good at detecting if patches are correct and if their own fixes are, too

# We would like to see if professionals are better at determining the correctness of their fixes and the patch
professional_correct_tab = table(full_df$professional_identity, full_df$accurate_about_correctness)
professional_patch_correct_tab = table(full_df_had_patch$professional_identity, full_df_had_patch$accurate_about_patch_correctness)
professional_correct_tab
professional_patch_correct_tab

test_prof_accuracy = chisq.test(professional_correct_tab)
test_prof_patch_accuracy = chisq.test(professional_patch_correct_tab)

test_prof_accuracy
test_prof_patch_accuracy

test_prof_accuracy$stdres
test_prof_patch_accuracy$stdres

# test also YOE
wilcox.test(professional_YOE ~ accurate_about_patch_correctness, 
            data = full_df_had_patch)
wilcox.test(professional_YOE ~ accurate_about_correctness, 
            data = full_df)

# Verdict: we do not have significant evidence to suggest this is the case.
```

# RQ4: How do patch suggestions influence cognitive load during debugging? (Section FIXME)
```{r}
# High level plan: do subjective reports from NASA-TLX, and then see if eye tracking metrics agree with the self-reports

# do model with self-reported predictors here
cognitive_load_model = lmer(cognitive_load ~ condition + professional_YOE
                              + java_intellij_experience + num_prev
                              + (1 | PID) + (1 | bug), 
                              data = full_df)

summary(cognitive_load_model)

# Redo significance testing
k1 <- glht(cognitive_load_model, mcp(condition="Tukey"))$linfct
k2 <- glht(cognitive_load_model, mcp(num_prev="Tukey"))$linfct
posthoc <- glht(cognitive_load_model, linfct = rbind(k1,k2))
summary(posthoc)
model_parameters(cognitive_load_model)
standardize_parameters(cognitive_load_model)

r2(cognitive_load_model)
Anova(cognitive_load_model)

# Gaze metrics related to cognitive load: average fixation duration
hist(gaze_valid_df$avg_fixation_duration)
# looks mostly normal to me, can use regular lmer
fix_duration_model = lmer(avg_fixation_duration ~ condition + (1|PID) + (1|bug), 
                          data = gaze_valid_df)
summary(fix_duration_model)

# Additionally, AFD is likely affected by when they looked at the patch first/how long they spent debugging unassisted
# So we can do an analysis separately
fix_duration_patch_model = lmer(avg_fixation_duration ~ condition + ttff_patch + (1|PID) + (1|bug), 
                          data = gaze_valid_had_patch)
summary(fix_duration_patch_model)
```

# Testing hypotheses for RQ2: What debugging strategies and behaviors distinguish successful from unsuccessful debugging attempts? (Section FIXME)
# Hypotheses derived from interview data
```{r}
# TODO: figure out survival analysis with anything where the outcome variable is time

# Hypothesis: people who look at the patch early on may be anchored to the patch's solution and may finish the task faster/more correctly
# expect condition:TTFF interaction ~ correctness and TTFF ~ time in glmer model
# random effect structure is non-estimable
# thus we do regular glm
# todo: ADD  back in bug
ttff_patch_model = glm(correct ~ ttff_patch + condition + bug, 
                 data = gaze_valid_had_patch, family = binomial)
summary(ttff_patch_model)

ttff_patch_model_time = lmer(time_minutes ~ ttff_patch + condition + (1|PID) + (1|bug), 
                 data = gaze_valid_had_patch)
summary(ttff_patch_model_time)
anova(ttff_patch_model_time)
table(gaze_valid_had_patch$correct)

# Hypothesis: Developers report triangulating multiple sources of information (tests, test output, code, patch, web-search) to debug, and prior work supports the idea that higher attention switching behavior correlates with effort and the accuracy of proof correction/problem-solving. Developers who exhibit higher attention switching behavior between AOIs may be more likely to debug correctly.
# look at number of cross-AOI switches / time ~ correctness
attention_switch_model = glmer(correct ~ attention_switching_rate + condition + (1|PID) + (1|bug),
                 data = gaze_valid_df, family = binomial)
summary(attention_switch_model)

attention_switch_model_time = lmer(time_minutes ~ attention_switching_rate + condition + (1|PID) + (1|bug),
                 data = gaze_valid_df)

# -------- #
# We are interested in seeing if focusing on any particular AOI predicts debugging correctness or speed beyond the treatment condition. We investigate with a series of  regressions and then compare for multcomp between outcome vars/same data
relevant_aoi_duration_cols = c("Test.and.Run.Output_fixation_duration", "Tests_fixation_duration", "Source.Code_fixation_duration", "Browser_fixation_duration")
# Patch_fixation_duration

# fill 0s for NAs in relevant AOI duration columns - they spent no time looking at these
gaze_valid_df[relevant_aoi_duration_cols][is.na(gaze_valid_df[relevant_aoi_duration_cols])] = 0
gaze_valid_had_patch[relevant_patch_aoi_duration_cols][is.na(gaze_valid_had_patch[relevant_patch_aoi_duration_cols])] = 0

relevant_aoi_prop_cols = paste0("prop_", relevant_aoi_duration_cols)
relevant_patch_aoi_prop_cols = paste0("prop_", relevant_patch_aoi_duration_cols)

# Create columns for the total fixation duration, then columns for duration proportion per AOI
gaze_valid_df$total_fixation_duration = rowSums(gaze_valid_df[, relevant_aoi_duration_cols])
gaze_valid_had_patch$total_fixation_duration = rowSums(gaze_valid_had_patch[, relevant_patch_aoi_duration_cols])
gaze_valid_df[, relevant_aoi_prop_cols] = gaze_valid_df[, relevant_aoi_duration_cols] / gaze_valid_df$total_fixation_duration
gaze_valid_had_patch[, relevant_patch_aoi_prop_cols] = gaze_valid_had_patch[, relevant_patch_aoi_duration_cols] / gaze_valid_had_patch$total_fixation_duration

# # Correctness: non-patch AOIs
# # list of models we're training and p-values for multcomp
# p_values = c()
# for (col in relevant_aoi_prop_cols) {
#   formula = as.formula(paste("correct ~", col, "+ condition + (1|PID) + (1|bug)"))
#   correct_model = glmer(formula, data = gaze_valid_df, family = binomial)
#   summary(correct_model)
# 
#   # save p-value for multcomp :3c
#   coef_table = summary(model)$coefficients
#   as.data.frame(coef_table)
#   # p_values[col] = coef_table[col, "Pr(>|z|)"]
# 
# }
# 
# p_adjusted = p.adjust(p_values, method = "BH")
# 
# data.frame(
#   aoi = relevant_aoi_prop_cols,
#   p_raw = p_values,
#   p_adjusted = p_adjusted
# )
# 
# # Correctness: patch AOI
# correct_patch_model = glmer(correct ~ prop_Patch_fixation_duration + condition + (1|PID) + (1|bug), data = gaze_valid_had_patch, family = binomial)
# summary(correct_patch_model)
# 
# # Timing: non-patch AOIs
# # FIXME: again, survival analysis?
# p_values_time = c()
# for (col in relevant_aoi_prop_cols) {
#   formula = as.formula(paste("time_minutes ~", col, "+ condition + (1|PID) + (1|bug)"))
#   time_model = lmer(formula, data = gaze_valid_df)
#   summary(time_model)
# 
#   # save p-value for multcomp :3c
#   coef_table = summary(model)$coefficients
#   p_values_time[col] = coef_table[col, "Pr(>|z|)"]
# }
# 
# p_adjusted_time = p.adjust(p_values_time, method = "BH")
# 
# data.frame(
#   aoi = relevant_aoi_prop_cols,
#   p_raw = p_values_time,
#   p_adjusted = p_adjusted_time
# )
# 
# # Timing: patch AOI
# time_patch_model = lmer(time_minutes ~ prop_Patch_fixation_duration + condition + (1|PID) + (1|bug), data = gaze_valid_had_patch)
# summary(time_patch_model)
```

# RQ3: How do patch suggestions influence developers' debugging strategies and behaviors? (Section FIXME)
```{r}
# Hypothesis: Overwhelmingly, developers report having access to a patch speeding up fault localization or making it possible for them. When developers have access to a patch, do they find the location of the bug faster, or find it at all? 
# TTFF on buggy method ~ has_patch
# check for subset of trials on Chart 12 -- this one had an overfitting patch that was not in the correct method
# First do logistic regression: did having a patch help people look at the buggy method more at all? 
# Then, see if it made them look at it faster
fl_model = glmer(looked_at_buggy_method ~ condition + (1|PID) + (1|bug), 
                 data = gaze_valid_df, family = binomial)
summary(fl_model)

fl_time_model = lmer(ttff_buggy_method ~ condition + (1|PID) + (1|bug),
                     data = gaze_valid_df)
summary(fl_time_model) # FIXME: look at residuals and try survival analysis if no good

# TODO: try simple test that is meant for small sample size to see if it also helped people find the bug with chart12 (which had wrong FL)

# Hypothesis: Along similar lines, developers also report having access to a patch narrowing their focus. When developers have access to a patch, do they look at a more narrow slice of a codebase or have a "pointier" distribution of attention?
# num_files_looked_at (should account for time confound), fixation_duration_entropy
# an offset just makes the coefficient 1, so creates assumption where there is a 1:1 relationship between the amount of time spent on task and the number of files you look at
num_files_m <- glmer(num_files_looked_at ~ condition + offset(log(time_minutes)) + (1|PID) + (1|bug), 
           data = gaze_valid_df, family = poisson)
summary(num_files_m)

entropy_m = lmer(fixation_duration_entropy ~ condition + (1|PID) + (1|bug), 
                 data = gaze_valid_df)
# ------ #
# We would like to see if distribution of attention changed over AOIs we care about with the addition of a patch
gaze_valid_df

gaze_valid_long <- gaze_valid_df %>%
  dplyr::select(PID, bug, condition, had_patch, all_of(relevant_aoi_prop_cols)) %>%
  pivot_longer(
    cols = all_of(relevant_aoi_prop_cols),
    names_to  = "AOI",
    values_to = "prop_fixation"
  ) %>%
  mutate(
    # Strip leading "prop_" and trailing "_fixation_duration"
    AOI = str_remove(AOI, "^prop_"),
    AOI = str_remove(AOI, "_fixation_duration$"),
    # Clean up dots in names like "Test.and.Run.Output" → "Test and Run Output"
    AOI = str_replace_all(AOI, "\\.", " "),
    # Convert to factors
    PID       = factor(PID),
    bug       = factor(bug),
    condition = factor(condition),
    AOI       = factor(AOI)
  )

gaze_valid_long
```

